Flowchart of Current Algorithm

### 2009-04-29 docs/flowchart/flowchart.tex
pass in gamma1bar^(1) instead of gamma1bar^{n+1,star} into the second call to advect base pressure

\item Update $p_0$ and compute $\psi$.
\begin{description}
\item For plane-parallel,\\
{\bf Advect Base Pressure Planar}$[p_0^n, w_0^{\nph}, \etarho^{n+\myhalf}]$ 
$\rightarrow [p_0^{n+1},\psi^{\nph}]$.
\item For spherical,\MarginPar{$\gammabar^{(1)}$ instead of $\gammabar^{n+1,\star}$?}\\
{\bf Advect Base Pressure Spherical}$[p_0^n,w_0^{\nph},\gammabar^{n+1,\star},\overline{S^{\nph}}] \rightarrow [p_0^{n+1},\psi^n,\psi^{\nph}]$.
\end{description}

>>>>

\item Update $p_0$ and compute $\psi$.
\begin{description}
\item For plane-parallel,\\
{\bf Advect Base Pressure Planar}$[p_0^n, w_0^{\nph}, \etarho^{n+\myhalf}]$ 
$\rightarrow [p_0^{n+1},\psi^{\nph}]$.
\item For spherical,\\
{\bf Advect Base Pressure Spherical}$[p_0^n,w_0^{\nph},\gammabar^{(1)},\overline{S^{\nph}}] \rightarrow [p_0^{n+1},\psi^n,\psi^{\nph}]$.
\end{description}
